---
title: "Reproducible Pitch: Analysis of MT cars"
author: "Sohini Mukherjee"
date: "18/02/2021"
output: slidy_presentation
html_document:
number_sections: yes
toc: yes
ioslides_presentation: default
mode: selfcontained
job: Reproducible Pitch Presentation
subtitle: Variables and MPG
highlighter: highlight.js
widgets: bootstrap
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models). You work for Motor Trend, a magazine about the automobile industry Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions: Is an automatic or manual transmission better for MPG. Quantify the MPG difference between automatic and manual transmissions.

## Format

A data frame with 32 observations on 11 variables.

- mpg Miles/(US) gallon

-	cyl	Number of cylinders

-	disp	Displacement (cu.in.)

-	hp	Gross horsepower

- drat	Rear axle ratio

- wt	Weight (lb/1000)

- qsec	1/4 mile time

- vs	V/S

- Am	Transmission (0 = automatic, 1 = manual)

- Gear	Number of forward gears

- Carb	Number of carburetors

## Data Summary

```{r}
library(datasets)
summary(mtcars)
```
## Analysis

```{r message=FALSE, warning=FALSE}
library(ggplot2)

mtcars$cyl <- as.factor(mtcars$cyl)
mtcars$vs <- as.factor(mtcars$vs)
mtcars$am <- factor(mtcars$am)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
attach(mtcars)
  boxplot(mpg ~ am, 
          xlab="Transmission Type (0 = Automatic, 1 = Manual)", 
          ylab="MPG",
          main="MPG by Transmission Type")

```
